---
title: "Title"
subtitle: "Subtitle"
author: "Noah Arias"
thanks: "Project repository available at: [https://github.com/ngarias/SJSU-STAT-257-Paper-1/tree/main](GitHub Repository)."
date: today
date-format: long
abstract: "An analysis on the linear predictability of the average goal differential per game."
format: pdf
bibliography: references.bib
number-sections: true
---

```{r}
#| include: false
#| warning: false
#| message: false
# load libraries
library(tidyverse)
library(nwslR)
library(ggpubr)
library(patchwork)

download.file("https://raw.githubusercontent.com/SCOREnetworkorg/sports-data-repository/main/data/nwsl-team-stats.csv", destfile = "nwsl-team-stats.csv")

nwsldata <- read.csv("nwsl-team-stats.csv")
```

# Introduction

In the United States of America (USA), the top professional women's soccer league is the [National Women's Soccer League](https://www.nwslsoccer.com/). It was established in 2012 as the successor to Women's Professional Soccer, and its scope of play is exclusively the USA. As of 2026, there are sixteen soccer teams present and all sixteen are present in the dataset used for this analysis. The dataset in question contains various types of statistics over each `

One of the key team metrics is its goal differential. It is defined as the difference between the number of goals scored by the team minus the number of goals scored by the opponent. In this data set, the number of goals scored by the opponent is refered to as goals conceded.

Since the goal differential metric is defined as the difference between the number of goals scored and number of goals scored upon, factors that go into either independent variable, such as passing and crossing accuracy, shot accuracy, and ball possession could be useful at predicting how successful a team was going to be in any given year.

In this report, we try and determine if there is a linear relationship that reasonably predicts average goal differential per game. 

# Data {#sec-data}
```{r}
#| echo: false
#| warning: false
#| message: false
#| fig-cap: "Linear regression on cross accuracy, goal conversion percentage, pass percentage, pass percentage on opposition half, posession percentage, shot accuracy, and tackle success percentage."

nwsldata <- nwsldata |>
  mutate(goal_diff_per_game = goal_differential / games_played)
```


# Methods {#sec-methods}



$$Y_i = \beta_0 +\beta_1 X_i + \varepsilon_i$$

# Results {#sec-results}

```{r}
#| echo: false
#| warning: false
#| message: false


```

```{r}
#| echo: false
#| warning: false
#| message: false
#| fig-cap: ""


```

# Discussion {#sec-discussion}

# References
